e9_altsAnalysis

### 2015-10-17 analysis/e11_analysis.Rmd
basic plot for prag listener judgments - need to implement output to .csv for RSA model

rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")

# commentary on weird RMarkdown bug
# https://github.com/hadley/xml2/issues/34
```

@@

# make sure to set directory path to 'production-results/e11/'
results_path = "sandbox-results/e11/"
files <- dir(results_path, pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste(results_path,f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answers$data$scale,
                   degree = jd$answers$data$degree,
                   stars = jd$answers$data$manipulation_level,
                   judgment = as.numeric(jd$answers$data$judgment),
                   language = jd$answers$data$language)
  d.raw <- bind_rows(d.raw, id)
}

@@

Let's remove training runs
```{r}
d.raw = d.raw[c(-1, -2), ]       # remove first two rows
d = d.raw %>% filter(scale != "training1")
```

Populate a new df
```{r}
ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            cnt.judgment = sum(judgment),
            speaker.p = mean(judgment)) 
```

Plot our literal listener semantic (counts data)
```{r}
pdf("plots/e10_L0Counts.pdf", width=8, height = 5)
qplot(x = stars, y = cnt.judgment, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = cnt.judgment - cil, 
                     ymax = cnt.judgment + cih)) + 
  facet_wrap(~scale) +
  ggtitle("Literal listener counts")
dev.off()

pdf("plots/e10_L0Percent.pdf", width=8, height = 5)
qplot(x = stars, y = speaker.p, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = speaker.p - cil, 
                     ymax = speaker.p + cih)) + 
  facet_wrap(~scale) +
  ggtitle("Literal listener percent 'yes'")
dev.off()
```

>>>>

rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")
# commentary on weird RMarkdown bug
# https://github.com/hadley/xml2/issues/34
```

@@

# make sure to set directory path to 'production-results/e11/'
results_path = "production-results/e11/"
files <- dir(results_path, pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste(results_path,f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answer$data$scale,
                   degree = jd$answer$data$degree,
                   stars = as.numeric(jd$answer$data$judgment),
                   language = jd$answer$data$language,
                   gender = jd$answers$data$gender,
                   age = jd$answers$data$age)
  d.raw <- bind_rows(d.raw, id)
}

@@

Let's remove training runs
```{r}
#d.raw = d.raw[c(-1, -2), ]       # remove first two rows
#d = d.raw %>% filter(scale != "training1")
```

Populate a new df
```{r}
density <- d %>%
  group_by(degree, scale) %>%
  mutate(n = n()) %>%
  group_by(degree, scale, stars) %>%
  summarise(prop = n() / n[1])
```

Plot our pragmatic listener judgments
```{r}
write.csv(density, "models/e11.csv", row.names=FALSE)
pdf("plots/e11.pdf", width = 8, height = 4)
qplot(stars, prop, facets = degree ~ scale, 
      geom="bar", stat = "identity",
      binwidth = 1, data=density)
dev.off()
```
